MachLensFinder - I: An automated Strong Lensing Identification Pipeline

### 2016-12-21 ms.tex
added all but final summary/discussino point on near misses

\item We have designed our pipeline to easily select and add image
  pre-processing and feature extraction methods, and to select a
  machine learning algorithm for classification.  Additionally, the
  user can easily perform parameter searches, and train a model with
  best parameters.

\item HOG efficiently extracts features that well-describe strong
  lensing systems with an arc. Performance of the model... SVM doesn't
  make a difference.

\item Ground based... noise... Model out BCG.

>>>>

\item We have designed our pipeline to easily select and add image
  pre-processing and feature extraction methods, and to select a
  machine learning algorithm for classification.  Additionally, the
  user can easily perform parameter searches to train a model with the
  best parameters for a given problem.

\item We have tested HOG as an efficient and effective feature
  extractor for galaxy-galaxy strong lensing systems in both a space
  based (HST-like) and ground based (LSST-like) observation.

\item We have found almost no difference between the Logistic
  Regression and Support Vector Machine algorithms, with Logistic
  Regression performing at a factor of $XX$ faster.  This means that
  features of lens and non-lens images are relatively well separated
  by hyperplanes in feature space.

\item We find AUC values of ROC curves of optimized classifier models
  to yield $AUC=0.987$ for the HST-like data, $AUC=0.96$ for the
  stacked LSST-like data with the lensing BCG included, and $AUC=0.86$
  for the stacked LSST-like data with the lensing BCG perfectly
  removed.  This suggests that we will be able to use our method to
  detect strong galaxy-galaxy lensing systems in future space-based
  missions (e.g. {\em Euclid}) with high purity and completeness.
  However, for future ground-based missions like LSST, we will need to
  perform additional image pre-processing, such as subtracting the
  image component corresponding to the lens.

\item Images that were difficult for our model to classify typically
  fell in the ..... ....
